MSAD_PCA_Walkthrough

### 2017-01-30 Simulation_Vignette.Rmd
Documentation completed for the mspMonitor function.

## Multi-State AD-PCA Implementation
We now throw all this data we've just generated into our package. CURRENT ISSUES: remove only alarmed observations, not flagged observations. Set up a replicate structure to repeat this proccess 1000 times.
```{r msad-pca}
Sys.time()
results_ls <- mvMonitoring::mspTrain(data = faults_ls$normal[,2:4],
                         labelVector = faults_ls$normal[,1],
                         trainObs = 4320,
                         updateFreq = 1440,
                         alpha = 0.001,
                         faultsToTriggerAlarm = 3,
                         lagsIncluded = 2)
Sys.time() # 14 seconds for 720 train, 360 update; 5 seconds for 1440, 720;
# 1 second for 2880 train (two days), and 1440 update (one day).

# Alarm code: 1 = T2 alarm; 2 = SPE alarm; 3 = both
falseAlarmRate_SPE <- sum(results_ls$FaultChecks[,5] %in% c(2,3)) /
  nrow(results_ls$FaultChecks)
# The SPE false alarm rate hits 0 at alpha = 0.07.
falseAlarmRate_T2 <- sum(results_ls$FaultChecks[,5] %in% c(1,3)) /
  nrow(results_ls$FaultChecks)
# The T2 false alarm rate hits 0 at alpha = 0.00015, and is at 16% at 0.07. The
# T2 statistic throws too many false alarms for my taste.
# These values were before we split the update observations by a third. These
# false alarm rates increased dramatically (0.19, 0.41), so we increased the 
# number of training observations to 4320 (three days worth, up from 2880). The
# false alarm rates dropped back, but not nearly as low (0.0031, 0.0884).
```

>>>>

## Multi-State AD-PCA Implementation
We now throw all this data we've just generated into our package.
```{r msad-pca}
Sys.time()
results_ls <- mvMonitoring::mspTrain(data = faults_ls$normal[,2:4],
                         labelVector = faults_ls$normal[,1],
                         trainObs = 4320,
                         updateFreq = 1440,
                         alpha = 0.001,
                         faultsToTriggerAlarm = 3,
                         lagsIncluded = 2)
Sys.time() # 14 seconds for 720 train, 360 update; 5 seconds for 1440, 720;
# 1 second for 2880 train (two days), and 1440 update (one day).

# Alarm code: 1 = T2 alarm; 2 = SPE alarm; 3 = both
(falseAlarmRate_SPE <- sum(results_ls$FaultChecks[,5] %in% c(2,3)) /
  nrow(results_ls$FaultChecks))
# The SPE false alarm rate hits 0 at alpha = 0.07.
(falseAlarmRate_T2 <- sum(results_ls$FaultChecks[,5] %in% c(1,3)) /
  nrow(results_ls$FaultChecks))
# The T2 false alarm rate hits 0 at alpha = 0.00015, and is at 16% at 0.07. The
# T2 statistic throws too many false alarms for my taste.
# These values were before we split the update observations by a third. These
# false alarm rates increased dramatically (0.19, 0.41), so we increased the 
# number of training observations to 4320 (three days worth, up from 2880). The
# false alarm rates dropped back, but not nearly as low (0.0031, 0.0884).
```

## Test the Multi-State Monitoring function
```{r test_msad-pca}
# Create six observations with lags 0:2 included
laggedTestObs <- faults_ls$normal[10073:10080, -1]
laggedTestObs <- stats::lag(laggedTestObs, 0:-2)
laggedTestObs <- cbind(faults_ls$normal[10073:10080, 1], laggedTestObs)
laggedTestObs <- laggedTestObs[-(7:8),]
testDataandFlags <- mspMonitor(observations = laggedTestObs[,-1],
           labelVector = laggedTestObs[,1],
           trainingSummary = results_ls$TrainingSpecs)
```
